---
title: "LogisticRegression"
output: github_document
---

```{r setup, include=FALSE}
#Logistic Regression

library(datasets)
library(ggplot2)
```

Logistic Regression
i. P = e^(β0 + β1X+ εi)/e^(β0 + β1X+ εi) +1.
ii. log(p/(1-p)) = β0 + β1X+ εi.
iii. log(p/(1-p)) is called the odds of probability. It is the probability of desired outcome being true divided by the probability of desired outcome not being true and this is called a logit function.
```{r}


Titanic_df<-data.frame(Titanic)
Titanic_df$Class<-as.factor(Titanic_df$Class)
regre<-glm(Survived~Class+Age+Sex+Freq,data=Titanic_df, family="binomial")
summary(regre)
```


```{r pred}

Y<-data.frame("Crew","Adult","Female",as.numeric("50"))

Y[2,]<-data.frame("1st","Adult","Female",as.numeric("50"))

Y[3,]<-data.frame("2nd","Adult","Female",as.numeric("50"))

Y[4,]<-data.frame("3rd","Adult","Female",as.numeric("50"))

names(Y)<-c("Class","Age","Sex","Freq")

Y$pred<-predict(regre,Y, type="response")
ggplot( Y, aes(x=Class, y=pred)) +
  geom_point() 

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
